### 2022-09-27 README.Rmd
Typos fixed.

This package contains both the data and the figures presented in the paper 
"Natural  Hazards Fatalities in Brazail, 1979–2019". Below is the abstract of the
aforementioned paper.

@@

This package contains two sets of data corresponding to fatalities by natural
hazards (one from 1979 to 1995 and the othre from 1996 to 2019), two datasets corresponding to Brazil's administrative divisions (state and town) and a last
dataset corresponding to a hexagonal approximation of the state division.

>>>>

This package contains both the data and the figures presented in the paper 
"Natural  Hazards Fatalities in Brazil, 1979–2019". Below is the abstract of the
aforementioned paper.

@@

This package contains:

- two datasets corresponding to fatalities by natural hazards (one from 1979 to 1995 
and the other from 1996 to 2019). 
- two datasets corresponding to Brazil's administrative divisions (state and town) 
- one dataset corresponding to a hexagonal approximation of the Brazilian state 
division.
